Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
non-atomic commit. Added little todos in multiple sections and switched ordering

\section{Design}
\noindent {\bfseries Overview}
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

At the start of the study, participants will be informed
of the role they they will be playing in the study. Particularly,
they will be informed that they are in a censorship environment
which prevents them from visiting certain websites, but they
are people who would like to visit those websites for 
leisurely purposes.

@@

\noindent {\bfseries Censorship Environment Simulation}
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

@@

@@

>>>>

\section{Design}

\noindent {\bfseries Overview}
% test tor, test improvements, may do followups on demand, push changes.

%improve what is below:
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

\noindent {\bfseries Experiment Flow} 
% explain one experiment from start to end. 
At the start of the study, participants will be informed
of the role they they will be playing in the study. Particularly,
they will be informed that they are in a censorship environment
which prevents them from visiting certain websites, but they
are people who would like to visit those websites for 
leisurely purposes.

@@

\noindent {\bfseries Censorship Environment Simulation}

We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

% talk about how these censorship environments cover the UI path

@@

%talk about how participants will be motivated to configure to 
%complete these tasks. participants will write down the answers 
%on a sheet of paper...

@@

% measure how an average user might configure Tor in various circumention settings
% test improvement and alternate configuration 
% make changes!
